Transform and Tell:\\The News Image Caption Writer That Remembers Rare Names

### 2019-11-08 paper/paper.tex
Work on related works

\usepackage{cvpr}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{multirow} % creates cells that span multiple rows in a table
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{booktabs}

@@

Most existing captioning systems can only generate a generic description of an
image \cite{Vinyals2015ShowAT, Fang2015FromCT, Karpathy2015DeepVA,
Rennie2017SelfCriticalST, Lu2017KnowingWT, Anderson2017BottomUpAT}, mainly
because these architectures cannot handle an open vocabulary and early
captioning datasets such as MS COCO \cite{Lin2014MicrosoftCC,
Chen2015MicrosoftCC} and Flickr30k \cite{Young2014FromID} were annotated using
only visual cues present in the image. More recently, datasets such as TIME
\cite{Tariq2017ACE}, BreakingNews \cite{Ramisa2016BreakingNewsAA}, and GoodNews
\cite{Biten2019GoodNews} include real-life captions written by professional
journalists. However, all existing models that are trained on these news
datasets use template-based methods to insert named entities.

@@

\begin{figure}[t]
   \begin{center}
   \fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
      %\includegraphics[width=0.8\linewidth]{egfigure.eps}
   \end{center}
      \caption{An example caption.}
   \label{fig:long}
   \label{fig:onecol}
\end{figure}

@@

Recent image captioning systems are based mostly on ``Show, Attend, Tell"
\cite{Xu2015ShowAA}, which uses a simple hard attention over the image. Later
improvements include giving the model the option to not attend to any image
region \cite{Lu2017KnowingWT}, using reinforcement learning to directly
optimize for the CIDEr metric \cite{Rennie2017SelfCriticalST}, and using a
bottom-up approach to propose a region to attend to
\cite{Anderson2017BottomUpAT}. All of these systems can only generate generic
captions with a limited vocabulary.

A more challenging task is to produce captions for news images, in which we
need to be able to generate entity names. There are non-neural approaches
\cite{Feng2013AutomaticCG,Tariq2017ACE}. Neural approaches include using the
word2vec representation of the article and and the VGG19 representation of the
image as context to the LSTM generator \cite{Ramisa2016BreakingNewsAA}.

Biten \etal~\cite{Biten2019GoodNews} further refined this approach by
developing a two-stage architecture to handle entity names. In the first stage,
the model generates a template with placeholders such as PERSON and
ORGANIZATION. In the second stage, the model finds the best matched sentence in
the article and replace the placeholder with an entity mentioned in that
sentence. They also created the ``GoodNews" dataset, which contains more
samples than MSCOCO and BreakingNews
\cite{Ramisa2016BreakingNewsAA} datasets.

Zhu \etal \cite{Zhu2018CaptioningTW} used transformers to achieve competitive
results on the MSCOCO dataset. Li \etal \cite{Li2019Boosted} added attention
over image regions and semantic concepts using Faster-RCNN
\cite{Ren2015FasterRCNN}. Both of these works, however, used the MSCOCO dataset
which contains generic captions with no named entities.

Wang \etal \cite{Wang2019Hierarchical} examined different strategies of
combining embeddings from three modalities: concept terms, object regions,
and image patches. These strategies include addition, concatenation, and
multivariate residual modules.

@@

\begin{table}[t]
	\caption {Summary of datasets}
	\label{tab:datasets}
	\centering
	\begin{tabular}{llll}
		\toprule
		  & GoodNews  & GoodNews+ &   NYTimes+ \\
		\midrule
      No. of articles & 241 808 & 241 808 & 445 828 \\
      No. of images   & 462 642 & 440 112 & 794 085 \\
      Article length & 451 & 963 & 974 \\
      Caption length & 18 & 18 & 18 \\
      Start month & Jan 10 & Jan 10 & Mar 05\\
      End month & Jul 18 & Jul 18 & Sep 19 \\
		\bottomrule
	\end{tabular}
\end{table}

@@

As a starting point, we use the GoodNews dataset, previously the largest
dataset on news image captioning. As part of the quality check, we also
reconstruct the same dataset on our own. We use the New York Times API and
write a custom parser to recollect and extract all the articles and images in
the same period as GoodNews from the original source. We call this GoodNews+.
We were able to crawl all the original articles, but the number of images is
slightly less, either due to dead links or not crawling images unrelated to the
main article. GoodNews+ allows us to make the following observations about the
original GoodNews dataset:

@@

>>>>

\usepackage{cvpr}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{multirow} % creates cells that span multiple rows in a table
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{booktabs}
\usepackage[export]{adjustbox} % adds a frame around figures

@@

Most existing captioning systems can only generate a generic description of an
image \cite{Donahue2015LongTR, Vinyals2015ShowAT, Fang2015FromCT,
Karpathy2015DeepVA, Rennie2017SelfCriticalST, Lu2017KnowingWT,
Anderson2017BottomUpAT, Cornia2019ShowCT}, mainly because these architectures
cannot handle an open vocabulary and early captioning datasets such as MS COCO
\cite{Lin2014MicrosoftCC, Chen2015MicrosoftCC} and Flickr30k
\cite{Young2014FromID} were annotated using only visual cues present in the
image. More recently, datasets such as TIME \cite{Tariq2017ACE}, BreakingNews
\cite{Ramisa2016BreakingNewsAA}, and GoodNews \cite{Biten2019GoodNews} include
real-life captions written by professional journalists. However, existing
models that are trained on these news datasets still need to rely on either
extractive methods or templates to insert named entities.

@@

\begin{figure}[t]
   \begin{center}
      \includegraphics[width=0.99\linewidth, frame]{figures/figure_1.pdf}
   \end{center}
      \caption{Our transformer model attends over embeddings from three
      different domains (image patches, faces, and article text). Using
      byte-pair encoding, the model can then directly produce a caption
      containing specific named entities without the use of templates.}
   \label{fig:long}
   \label{fig:onecol}
\end{figure}

@@

Early image captioning systems mainly used an RNN architecture with a closed
vocabulary \cite{Karpathy2015DeepVA, Donahue2015LongTR, Vinyals2015ShowAT}.
Attention over image patches was later introduced in ``Show, Attend and Tell"
\cite{Xu2015ShowAA}, in which the attention weights are obtained by feeding the
image embeddings and the previous hidden state of the RNN through a multilayer
perception. Later improvements include giving the model the option to not
attend to any image region \cite{Lu2017KnowingWT}, using reinforcement learning
to directly optimize for the CIDEr metric \cite{Rennie2017SelfCriticalST}, and
using a bottom-up approach to propose a region to attend to
\cite{Anderson2017BottomUpAT}. All of these systems can only generate generic
captions with a limited vocabulary.

A more challenging task is to produce captions for news images, in which we
need to be able to generate entity names. Early non-neural approaches include
extractive methods that use n-gram models to combine existing phrases
\cite{Feng2013AutomaticCG} or simply retrieving the most representative
sentence \cite{Tariq2017ACE} in the article. Ramisa \etal
\cite{Ramisa2016BreakingNewsAA} concatenated the word2vec representation of the
article and and the VGG19 representation of the image, and feed them as inputs
to an LSTM generator. However the generator still cannot produce names not
seen in training.

To overcome the limitation of a fixed-size vocabulary, template-based methods
have been used to insert named entities. This involves first generating a
template sentence with placeholders, e.g. ``PERSON speaks at BUILDING in
DATE.'' Afterwards, a selection algorithm is used to pick the best candidate
for each placeholder. Lu \etal \cite{Lu2018EntityAI} built a knowledge graph
for each combination of entities and select the most likely combination.
Meanwhile Biten \etal~\cite{Biten2019GoodNews}, whose GoodNews dataset we will
benchmark against, picked the sentence with the highest cosine similarity with
the template and then found the first entity that matches the type of each
placeholder for insertion. Our proposed model differs from
\cite{Lu2018EntityAI} and \cite{Biten2019GoodNews} in that we are able to
generate a caption with named entities directly without using any intermediate
template.

Transformers are still scarcely used in image captioning. They have been shown
to yield competitive results in generating generic MS COCO captions
\cite{Zhu2018CaptioningTW, Li2019Boosted}. Zhao \etal
\cite{Zhao2019InformativeIC} have gone further and train transformers to
produce named entities in the Conceptual Captions dataset
\cite{Sharma2018ConceptualCA}. However Conceptual Captions have no additional
context apart from the image itself, and the authors use web-entity labels,
extracted using Google Cloud Vision API, as inputs to the model. In our work,
we are more ambitious in that we do not explicitly give the model a list of
entities that should appear in the caption. Instead the model has to determine
which entities to generate on its own by scanning through and attending to the
article.

BPE offers an elegant solution to handle an open vocabulary. To date the only
image captioning work that uses BPE is \cite{Sharma2018ConceptualCA}, but in
their data preprocessing step, they explicitly removed rare named entities from
the captions. Thus no study has been done yet to see how well BPE used in
transformers can generate rare names.

In addition to attending to image patches, some captioning models attend to
objects \cite{Wang2019Hierarchical} and concept terms
\cite{Wang2019Hierarchical,Li2019Boosted}, both of which are derived from the
image itself. When attending to more than one modality, there are various
strategies on how to combine embeddings such as addition, concatenation, and
using multivariate residual modules \cite{Wang2019Hierarchical}.

@@

@@

As a starting point, we use the GoodNews dataset, previously the largest
dataset on news image captioning \cite{Biten2019GoodNews}. As part of the
quality check, we also reconstruct the same dataset on our own. We use the New
York Times API and write a custom parser to recollect and extract all the
articles and images in the same period as GoodNews from the original source. We
call this GoodNews+. We were able to crawl all the original articles, but the
number of images is slightly less, either due to dead links or not crawling
images unrelated to the main article. GoodNews+ allows us to make the following
observations about the original GoodNews dataset:

@@

\begin{table}[h]
	\caption {Summary of datasets}
	\label{tab:datasets}
	\centering
	\begin{tabular}{llll}
		\toprule
		  & GoodNews  & GoodNews+ &   NYTimes+ \\
		\midrule
      No. of articles & 241 808 & 241 808 & 445 828 \\
      No. of images   & 462 642 & 440 112 & 794 085 \\
      Article length & 451 & 963 & 974 \\
      Caption length & 18 & 18 & 18 \\
      Start month & Jan 10 & Jan 10 & Mar 05\\
      End month & Jul 18 & Jul 18 & Sep 19 \\
		\bottomrule
	\end{tabular}
\end{table}
